Dirac neutrino mass generation from Majorana messenger

### 2019-07-09 draft.tex
Updates from Overleaf

\section{Introduction}
\label{sec:intro}
%Dirac vs Majorana (From previous paper: must be rephrased
The interpretation of neutrino experimental data in terms of neutrino
oscillations is compatible with both Majorana or Dirac neutrino masses
\cite{Tanabashi:2018oca}. The former possibility has received the most
attention but, given the lack of signals in neutrinoless double beta
decay experiments
\cite{KamLAND-Zen:2016pfg,Agostini:2018tnm,Aalseth:2017btx,Alduino:2017ehq,Albert:2017owj,Arnold:2016bed},
the latter cannot be dismissed. If neutrinos are Dirac particles, the
Standard Model (SM) particle content must be extended with
right-handed neutrinos, which can increase the number the effective
number light neutrinos, $N_{\text{eff}}$, until 6. To give small
masses to at least two Majorana or Dirac neutrinos, as required to
explain the neutrino oscillation experiments~\cite{Ahmad:2002jz,
  Fukuda:1998mi}, the seesaw mechanism with heavy fermions is usually
invoked.

Discussion: At three level seem to have that we can have also all Majorana mediators for Dirac neutrinos. See plot:

\includegraphics[scale=0.5]{tl}

>>>>

\section{Introduction}
\label{sec:intro}
%Dirac vs Majorana (From previous paper: must be rephrased
The interpretation of neutrino experimental data in terms of neutrino
oscillations is compatible with both Majorana or Dirac neutrino masses
\cite{Tanabashi:2018oca}. The former possibility has received the most
attention but, given the lack of signals in neutrinoless double beta
decay experiments
\cite{KamLAND-Zen:2016pfg,Agostini:2018tnm,Aalseth:2017btx,Alduino:2017ehq,Albert:2017owj,Arnold:2016bed},
the latter cannot be dismissed. If neutrinos are Dirac particles, the
Standard Model (SM) particle content must be extended with
right-handed neutrinos, which can increase the number the effective
number light neutrinos, $N_{\text{eff}}$, until 6. To give small
masses to at least two Majorana or Dirac neutrinos, as required to
explain the neutrino oscillation experiments~\cite{Ahmad:2002jz,
  Fukuda:1998mi}, the seesaw mechanism with heavy fermions is usually
invoked. For the tree-level type-I seesaw we can have either light Majorana neutrinos with heavy Majorana mediators~\cite{} or light Dirac neutrinos with heavy Dirac mediators~\cite{} (see provisional figure below). The radiative type-I seesaw includes these both possibilities:~\cite{} and \cite{}, but now it is possible also to have also Majorana fermions with Dirac mediators. In this
work we want to explore the possibility to build a simple model with
Dirac masses and Majorana mediators.

%TO BE DELETED
Preliminary discussion: At three level a Dirac seesaw with Majorana mediators automatically allows for Majorana masses, as illustrated in the provisional plot: neutrinos. See plot:

\includegraphics[scale=0.4]{tl}
